\documentclass[a4paper,11pt]{letter}
\usepackage[lmargin=20mm, rmargin=20mm]{geometry}
\usepackage{tabularx}
\usepackage[hidelinks]{hyperref}

\begin{document}
\signature{Ada Stevenson}
\address{216 Lake Street \\ Perth 6000 WA \\ Australia}

\begin{letter}{
    15-17 William Street\\
    Level 6 Australia Place\\
    Perth 6000\\
    Western Australia
  }
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Ada Stevenson} & Mobile : \href{tel:+61478961246}{+61-478-961-246}\\
  (she/they) & Email : \href{mailto:ada.stevenson26@gmail.com}{ada.stevenson26@gmail.com} \\
\end{tabular*}


\opening{Dear Marcela Alencar,}

The work Hexagon is doing in the embedded systems field is highly impressive - drive-by-wire is an engineering problem that combines requires knowledge of low-level hardware to design sensor arrays and drive-by-wire controller systems, whilst also requiring high-level software engineering knowledge to create spatial awareness in the autonomous vehicle. A project like this is the perfect way to immerse myself into the field of Embedded Engineering.

I believe I will make an excellent addition to your drive-by-wire team. I have a strong, fundamental understanding of software engineering from my personal projects, and I'm currently studying the fundamental concepts of electronics design and electrical engineering. My solid grasp of C combined with my knowledge of high-level concepts in languages such as Common Lisp put me in a great position to begin learning C++ as it exists in the embedded field.

Hexagon prides itself as a diverse and inclusive company, which is one of the things that attracts me to it so much. I want to learn and grow as an engineer, first and foremost; Hexagon is a company that values this just as much as me. I'm great at communicating my ideas to others, and highly value teamwork and working collaboratively. I believe I would be a fantastic fit for your team - a company as highly international as Hexagon needs people who can collaborate easily and communicate with clarity.

Interning at Hexagon would be such a enriching experience for me and my engineering career. The work your company is doing in the field of autonomous vehicles is truly groundbreaking, and I would relish the chance to be a part of it. I'm excited to hear back from you regarding my qualifications.

\closing{Thank you for your consideration,}

\end{letter}


\end{document}
