%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Ada Stevenson} & Mobile : \href{tel:+61478961246}{+61-478-961-246}\\
  (she/they) & Email : \href{mailto:ada.stevenson26@gmail.com}{ada.stevenson26@gmail.com} \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
    {Curtin University}{Perth, Western Australia}{Bachelor of Electric and Electronic Engineering}{Feb. 2022 -- Projected Jul. 2026}
    \begin{itemize}
      \item\small{Specialising in the Embedded Systems stream.}
      \item\small{Developing knowledge in:
            \begin{itemize}
              \item\small{Complex circuit design and analysis}
              \item\small{Integrated circuit design}
              \item\small{Embedded development environments, writing bare-metal C and assembly language}
              \item\small{Systems programming and Operating Systems design}
                    \end{itemize}}
    \end{itemize}
    \resumeSubheading
      {Christian Brothers College}{Fremantle, Western Australia}
      {Completed ATAR pathway}
{Feb. 2016 -- Nov. 2021}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {LessPain4Life}{Claremont, WA}
      {Medical Administrator}{Jun 2023 - Present}
      \resumeItemListStart
        \resumeItem{Automated Report Formatter}
          {Developing a report-fixing tool in Common Lisp that manipulates HTML trees and performs programmable, structure aware changes to format reports appropriately. In the making of this tool, I implemented a simple parser using parser combinators, transforming style strings into manipulatable data.}
        \resumeItem{Asynchronous Collaboration}
        {Developed skills for collaborating online and in an asynchronous environment. Can manage time independently, allocating resources to ensure key objectives are completed on-time.}
      \resumeItemListEnd

    \resumeSubheading
      {The Quarter Acre Hotel}{Applecross, WA}
      {Maintainence and Wait Staff}{Dec 2019 - Jun 2023}
      \resumeItemListStart
      \resumeItem{Customer Attentiveness}
      {Learned key skills for operating in a fast-moving workspace, including: situational awareness, initiative and attention to detail.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Guix Maintainence}
    {Help maintain certain packages for GNU Guix, a transactional, immutable Linux distribution configurable in Guile Scheme.}
    \resumeSubItem{LessPain Report Fixer}
    {Programmable, structure aware report formatter written in Common Lisp.}
    \resumeSubItem{Langton's Ant Simulation}
    {Langton's Ant simulation written in C, exhibiting a consistent API for manipulating actors and the game board.}
  \resumeSubHeadingListEnd

  \section{Skills}
  \resumeSubHeadingListStart
  \resumeSubItem{Programming Proficiency}
  {Exceptionally sound foundation in computing, with familiarity and experience in:
    \begin{itemize}
      \item{the Linux/POSIX environment.}
      \item{programming in C, Python, Common Lisp, Guile Scheme.}
      \item{common data structures and algorithms.}
      \item{debugging techniques and tools such as GDB and Valgrind.}
      \item{fundamental principles of object-oriented, functional and imperative programming paradigms.}
    \end{itemize}}
  \resumeSubItem{Passion for Technology}
  {\begin{itemize}
     \item{Deeply passionate about technology and computing systems in various domains.}
     \item{Self-motivated learner with a keen interest in staying up-to-date with the latest advancements in the field.}
   \end{itemize}}
 \resumeSubItem{Communication and Teamwork}
 {\begin{itemize}
    \item{Excellent communication skills, both written and verbal, facilitating effective collaboration with team members.}
  \end{itemize}}
\resumeSubItem{Problem-solving Abilities}
{\begin{itemize}
   \item{Strong analytical and problem-solving skills, honed through academic and extracurricular projects.}
   \item{Ability to break down problems into easy to undertstand and implement stages.}
         \end{itemize}}
\resumeSubHeadingListEnd
%-------------------------------------------
\end{document}
